Harmony: A Systems Programming Language and Model Checker

### 2022-01-16 paper/paper.tex
Latest
Fixed active busy wait

def release(lk):
    atomically:
        if lk->blocked == []:
            lk->held = False
        else:
            go (list.head(lk->blocked)) ()
            lk->blocked = list.tail(lk->blocked)
<{:end:}>
\end{code}
}
\end{center}
\caption{FIFO lock using continuation}
\label{fig:continuation}
\end{figure}

@@

A thread is considered \emph{actively busy waiting} if it cannot
escape its strongly connected component without another thread
updating the shared state first.  A common example of this is a
synchronization algorithm that checks for a condition in a loop,
acquiring and releasing the lock each time.  Harmony checks each
strongly connected component for the existence of such situations
and reports the shortest example.

>>>>

def release(lk):
    atomically:
        if lk->blocked == []:
            lk->held = False
        else:
            go (list.head(lk->blocked)) ()
            lk->blocked = list.tail(lk->blocked)
<{:end:}>
\end{code}
}
\end{center}
\caption{FIFO lock using continuations}
\label{fig:continuation}
\end{figure}

@@

A thread is considered \emph{actively busy waiting} if it is in a
loop updating the shared state, but cannot
escape its strongly connected component without another thread
also updating the shared state.  A common example of this is a
synchronization algorithm that checks for a condition in a loop,
acquiring and releasing the lock each time.  Harmony checks each
strongly connected component for the existence of such situations
and reports the shortest example.
